Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI~837: A Young Validated Planet in IC~2602

### 2020-07-28 paper/ms.tex
update manuscript
Co-authored-by: Chris Tinney <c.tinney@unsw.edu.au>

A number of other processes are expected to shape young exoplanets.
After accreting, planets with gaseous envelopes are thought to cool
and contract, and their atmospheres are expected to undergo a mix of
photoevaporation and core-powered mass loss \citep[{\it
e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017,gupta_sculpting_2019,gupta_signatures_2020}.
Reported timescales for photoevaporation and core-powered mass loss
range from 10$\,$Myr to over 1$\,$Gyr for typical transiting
sub-Neptunes
\citep{ginzburg_superearth_2016,owen_evaporation_2017,king_euv_2020}.
The relative importance of each process is set by the planetary surface
gravity and the radiation environment.  Both processes can be
directly observed through observations of planetary winds in the
metastable 1083$\,$nm He line
\citep{spake_helium_2018,oklopcic_new_2018,mansfield_detection_2018}.

@@

A few dozen planets in clusters have been detected, and fewer still
have been closely characterized.  Despite the challenges of
starspot-induced radial velocity (RV) variations, RV surveys found
success in the Hyades, NGC~2523, Praesepe, and M~67
\citep{Sato_et_al_2007,lovis_mayor_2007,Quinn_et_al_2012,Malavolta_et_al_2016,brucalassi_search_2017}.
RV surveys of highly active pre-main sequence stars in Taurus also led
to the youngest hot Jupiters yet reported orbiting V830~Tau, TAP~26, and
CI~Tau
\citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.
%Follow-up by Damasso et al{.} (2020, submitted) did not detect
%the planetary signal in V830~Tau.

@@

The transits of \pn\ are grazing, which is a cause for concern.
Particularly for a target near the galactic plane ($b=-5.8^\circ$),
background eclipsing binaries are a major source of astrophysical
false positives \citep[{\it e.g.},][Figure~30]{Sullivan_2015}.  Our
follow-up data show that this and related scenarios are unlikely to
the degree that we can ``validate'' the planet, {\it i.e.}, determine
that its probability of being an astrophysical false positive is
negligibly small.  We considered this result worth reporting because
of the planet's youth.

@@

Figure~\ref{fig:tessphot} shows the data.  The dominant modulation
induced by starspots coming into and out of view has a peak-to-peak
amplitude of about 2.3\%, and a period of about 3 days.  The dips
suggestive of a grazing transiting planet recur roughly every 8 days,
and have a depth of about 0.4\%.  A few flares are also visible.  A
phase-folded view of the TESS transits with starspot variability
removed is shown in Figure~\ref{fig:tessphot}. Our fitting procedure
for the models shown in these plots is described in
Section~\ref{subsec:planet}.

@@

\subsubsection{Veloce}
We acquired 34 spectra over 10 visits of \tn\ using the Veloce
spectrograph, mounted on the AAT 3.9$\,$m telescope at Siding Spring
Observatory near Coonabarabran, Australia \citep{gilbert_veloce_2018}.
In the ``Rosso'' instrument-mode, Veloce provides coverage from
600--950$\,$nm at a spectral resolution of $\approx 80{,}000$.  Many
of the exposures were taken in average or poor seeing conditions, when
fiber-to-fiber cross-contamination on the IFU-style fiber feed is
strongest.  To reduce the spectra to velocities, we cross-correlated
against a high S/N template of $\delta$ Pavonis, because with spectral
type G8 IV it was the closest \tn\ analog available in the Veloce
spectral database.  The velocity RMS seen across each visit was
hundreds of meters per second, likely due to uncorrected
fiber-to-fiber cross-contamination.  For analysis purposes, we
averaged across each visit, and set the velocity uncertainties to be
the standard deviation of the per-visit exposures.  The velocities are
given in Table~\ref{tab:rvs}, and shown in Figure~\ref{fig:followup}.

@@

A.J.\ and R.B.\ acknowledge support from project IC120009 ``Millennium
Institute of Astrophysics (MAS)'' of the Millenium Science Initiative,
Chilean Ministry of Economy. A.J.\ acknowledges additional support
from FONDECYT project 1171208.  J.I.V\ acknowledges support from
CONICYT-PFCHA/Doctorado Nacional-21191829.
R.B.\ acknowledges support from FONDECYT Post-doctoral Fellowship Project 3180246.
%
C.Z.\ is supported by a Dunlap Fellowship at the Dunlap Institute for
Astronomy \& Astrophysics, funded through an endowment established by
the Dunlap family and the University of Toronto.
%

>>>>

A number of other processes are expected to shape young exoplanets.
After accreting, planets with gaseous envelopes are thought to cool
and contract, and their atmospheres are expected to undergo a mix of
photoevaporation and core-powered mass loss \citep[{\it
e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017,gupta_sculpting_2019,gupta_signatures_2020}.
Predicted timescales for photoevaporation and core-powered mass loss
range from 10 million years to over 1 gigayear for typical transiting
sub-Neptunes
\citep{ginzburg_superearth_2016,owen_evaporation_2017,king_euv_2020}.
The relative importance of each process is set by the planetary surface
gravity and the radiation environment.  Both processes can be
directly observed through observations of planetary winds in the
metastable 1083$\,$nm He line
\citep{spake_helium_2018,oklopcic_new_2018,mansfield_detection_2018}.

@@

A few dozen planets in clusters have been detected, and fewer still
have been closely characterized.  Despite the challenges of
starspot-induced radial velocity (RV) variations, RV surveys found
success in the Hyades, NGC~2523, Praesepe, and M~67
\citep{Sato_et_al_2007,lovis_mayor_2007,Quinn_et_al_2012,Malavolta_et_al_2016,brucalassi_search_2017}.
RV surveys of highly active pre-main sequence stars in Taurus also led
to the youngest hot Jupiters yet reported orbiting
V830~Tau\footnote{Follow-up by Damasso et al{.} (2020, submitted) did
not detect the planetary signal in V830~Tau.}, TAP~26, and CI~Tau
\citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.

@@

The transits of \pn\ are grazing the stellar limb, which is a cause
for concern.  Particularly for a target near the galactic plane
($b=-5.8^\circ$), background eclipsing binaries are a major source of
astrophysical false positives \citep[{\it
e.g.},][Figure~30]{Sullivan_2015}.  Our follow-up data show that this
and related scenarios are unlikely to the degree that we can
``validate'' the planet, {\it i.e.}, determine that its probability of
being an astrophysical false positive is negligibly small.  We
considered this result worth reporting because of the planet's youth.

@@

Figure~\ref{fig:tessphot} shows the data.  The dominant modulation
induced by starspots coming into and out of view has a peak-to-peak
amplitude of about 2.3\%, and a period of about 3 days.  The dips are
suggestive of a grazing transiting planet, recurring roughly every 8
days with a depth of about 0.4\%.  A few flares are also visible.  A
phase-folded view of the TESS transits with starspot variability
removed is shown in Figure~\ref{fig:tessphot}. Our fitting procedure
for the models shown in these plots is described in
Section~\ref{subsec:planet}.

@@

\subsubsection{Veloce}
We acquired 34 spectra over 10 visits of \tn\ using the Veloce
spectrograph, mounted on the 3.9$\,$m Anglo-Australian Telescope at
Siding Spring Observatory near Coonabarabran, Australia
\citep{gilbert_veloce_2018}.  Veloce's currently implemented Rosso
camera provides coverage from 600--950$\,$nm at a spectral resolution
of $\approx 80{,}000$.  Many of the exposures were taken in average or
poor seeing conditions, when fiber-to-fiber cross-contamination on the
IFU-style fiber feed is strongest.  To reduce the spectra to
velocities, we cross-correlated against a high S/N template of
$\delta$ Pavonis, because with spectral type G8 IV it was the closest
\tn\ analog available in the Veloce spectral database.  The velocity
RMS seen across each visit was hundreds of meters per second, likely
due to uncorrected fiber-to-fiber cross-contamination.  For analysis
purposes, we averaged across each visit, and set the velocity
uncertainties to be the standard deviation of the per-visit exposures.
The velocities are given in Table~\ref{tab:rvs}, and shown in
Figure~\ref{fig:followup}.

@@

A.J.\ and R.B.\ acknowledge support from project IC120009 ``Millennium
Institute of Astrophysics (MAS)'' of the Millenium Science Initiative,
Chilean Ministry of Economy. A.J.\ acknowledges additional support
from FONDECYT project 1171208.  J.I.V\ acknowledges support from
CONICYT-PFCHA/Doctorado Nacional-21191829.  R.B.\ acknowledges support
from FONDECYT Post-doctoral Fellowship Project 3180246.
%
C.T.\ and C.B\ acknowledge support from Australian Research Council
grants LE150100087, LE160100014, LE180100165, DP170103491 and
DP190103688.
%
C.Z.\ is supported by a Dunlap Fellowship at the Dunlap Institute for
Astronomy \& Astrophysics, funded through an endowment established by
the Dunlap family and the University of Toronto.
%
